%-------------------------
% Cv in Latex
% Author : Mostafa Abdelgawad
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{soul} % for the \hl command
% Flexible tables
\usepackage{tabu}
\usepackage{multirow}
\usepackage{enumitem}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{0pt}\scshape\raggedright\large
}{}{0pt}{}[\color{black}\titlerule \vspace{0pt}]

%-------------------------
% Custom commands
\newcommand{\CvItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\CvSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\CvSubheadingWithoutTitle}[3]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \multirow{2}{*}{\textbf{#1}} & #2 \\
     & \textit{\small #3} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\CvSubSubheadingWithoutTitleAndDate}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    {\textbf{#1}} & #2 \\
    \end{tabular*}\vspace{-10pt}
}

\newcommand{\CvSubItem}[2]{\CvItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\CvSubHeadingListStart}{\begin{itemize}[leftmargin=*,topsep = 0pt]}
\newcommand{\List}{\begin{itemize}[topsep = 0pt, itemsep = -1pt]}
\newcommand{\CvSubHeadingListEnd}{\end{itemize}}
\newcommand{\EndList}{\end{itemize}}
\newcommand{\CvItemListStart}{\begin{itemize}}
\newcommand{\CvItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%--------------------------------------------------------------------------------
%                            Header Setup and Printing                          -
%--------------------------------------------------------------------------------

% Address
\makeatletter

\newcommand\address[1]{\def\@address{#1}}
\address{}

\newcommand\printaddress{
	\small{\@address}
}

% Webpage
\makeatletter

\newcommand\linkedin[1]{\def\@linkedin{#1}}
\linkedin{}

\newcommand\printlinkedin{
	\small{\@linkedin}
}

\makeatother

% Name
\makeatletter

\newcommand\name[1]{\def\@name{#1}}
\name{}

\newcommand\printname{
	\textbf{\LARGE{\textsc{\@name}}}
}

\makeatother

% Contacts
\makeatletter

\newcommand\contacts[1]{\def\@contacts{#1}}
\contacts{}

\newcommand\printcontacts{
	\small{\@contacts}
}

\makeatother

% Github
\makeatletter

\newcommand\github[1]{\def\@github{#1}}
\contacts{}

\newcommand\printgithub{
	\small{\@github}
}

\makeatother

%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Set applicant's personal data for header
\name{Mostafa Abdelgawad}
\address{166 E Horus, Pyramids' Gardens \linebreak Giza, Egypt 12556}
\linkedin{\href{https://www.linkedin.com/in/mostafaelgawad/}{linkedin.com/in/mostafaelgawad}}
\contacts{Mobile : +201129216108 \linebreak \href{mailto:elgawad.mostafa@gmail.com}{elgawad.mostafa@gmail.com} }
\github{\href{https://github.com/MostafaElgawad}{github.com/MostafaElgawad}}

\begin{document}

%----------HEADING-----------------
\begin{center}
    \begin{tabu} to 1\textwidth {X[l,m] X[1,c,m] X[r,m] }
        \printaddress \printlinkedin & \printname & \printcontacts
        \printgithub \\
    \end{tabu}
\end{center}


%-----------EDUCATION-----------------
\section{Education}
  \CvSubHeadingListStart
    \CvSubheading
      {\href{https://eng.cu.edu.eg/en/}{Cairo University, Faculty of Engineering}}{Giza, Egypt}
      {Bachelor of Engineering in Communications and Computer;  GPA: 3.31}{Sep. 2015 -- May. 2020}
  \CvSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Work Experience}
  \CvSubHeadingListStart

    \CvSubheading
      {APTIV (EJAD B.O.T. program)}{Free Zone, Naser City}
      {Embedded Systems Software Engineer}{Oct 2022 - Present}
      \CvItemListStart
        \CvItem
        { {MPIC (Multi-Purpose Interior Camera)}\\\textit{part of Daimler's CIVIC "central In vehicle infotainment computer" project}}
          {\List
          \item Developed APIs used by testing tool "Test Commander" in Python.
          \item Tested the software in level of SWE.5 "Integration" \& SWE.6 "Qualification" testing following ASPICE model.
          \EndList}
      \CvItemListEnd

    \CvSubheading
      {Cairo University, Faculty of Engineering}{Giza, Egypt}
      {Teaching assistant}{Oct 2021 - Jun 2022}
      \CvItemListStart
        \CvItem{Programming Techniques course}
          {\List
            \item Co-instructed C++ basics and function versus object-oriented programming.
            \item Evaluated students' assignments and quizzes.
            \EndList}
        \CvItem{Data Structures \& Algorithms course}
          {\List
            \item Co-instructed data structures representations in storage media and memory allocation.
            \item Co-instructed searching and sorting algorithms.
            \EndList}
        \CvItem{Advanced Programming Techniques course}
          {\List
            \item Co-instructed Programming Techniques in Network and various Media Types (e.g multithreaded programming, Internet programming).
            \EndList}
      \CvItemListEnd

    \CvSubheading
      {Advansys ESC}{Free Zone, Naser City}
      {RPA developer intern}{Sep 2020 - Mar 2021}
      \CvItemListStart
      \CvItem{Bupa}
      {Supported in the maintanace of deployed robots using UiPath, Blue Prism, and Automation Anywhere framworks.}
      \CvItemListEnd   
  \CvSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Academic Projects}
  \CvSubHeadingListStart
    \CvSubItem{\href{https://www.youtube.com/watch?v=Qrf6ohhCA0c&feature=youtu.be}{Lipify - Lip Reading Application, Graduation Project}}
        {\List
            \item Developed a system that can predict the user's words based on selected categories and using only lips movements.
            \item Built a lips recognition module using image processing in python.
            \item Implemented a feature extraction module using DCT and LDA.
        \EndList}
    \CvSubItem{\href{https://github.com/amrkh97/Arabic-OCR-Using-PythonURL}{Arabic Optical Character Recognizer, Pattern Recognition Course}}
        {\List
            \item Built an offline OCR system using TensorFlow; depending only on classical approaches to extract features.
        \EndList}
    \CvSubItem{\href{https://github.com/amrkh97/FifaPredictor-BigData}{FIFA Analyzer, Big Data Course}}
        {\List
            \item Provided meaningful insights and analysis of clubs, age distribution among top valued clubs, and superstars skills.
            \item Built a linear Regression Model using R to predict player’s market value.
            \item Built a Polynomial and Linear Regression Models using R to predict player’s wage.
        \EndList}
    \CvSubItem{\href{https://github.com/AhmedSalemElhady/Scrabble-Game.ai}{Scrabble Engine, Machine Intelligence Course}}
        {\List
            \item Developed an intelligent agent that plays the scrabble board game.
            \item Integreted and tested the Monte-Carlo Module in the system.
        \EndList}
    \CvSubItem{\href{https://github.com/ahmedHusseinF/emojicode}{EmojiCode, Compilers Course}}
        {\List
            \item Implemented a lexer, parser, and compiler for a language of emojis using Lex and YACC.
        \EndList}
  \CvSubHeadingListEnd

%
%---------Additional Experience and Awards--------
%
\section{Additional Experience and Awards}
    \CvSubHeadingListStart
        \CvSubheadingWithoutTitle
        {CURT Cairo University Racing Team}{Cairo University}
        {Sep 2019 - Jun 2020 }
            {\begin{itemize}[topsep = -5pt, itemsep = -2pt]
                \item Participated in Formula Students Competition 2020.
                \item Built the main dashboard and failure system.
            \end{itemize}}
    \CvSubheadingWithoutTitle
        {Embedded Systems Diploma}{Eng. Mohamed Tarek}
        {Sep 2019 - Jun 2020 }
            \begin{itemize}[topsep = -5pt, itemsep = -2pt]
                \item Studied Embedded C, AVR Micro-controllers Interfacing, and RTOS.
                \item Built a door locking security system using TivaC.
                \begin{itemize}[topsep = -1pt]
                    \item Implemented a Security System consists of two ECU’s. HMI which is responsible for interfacing with 
                    the user and control ECU which is responsible for the system operations and control.
                \end{itemize} 
            \end{itemize}
    \CvSubSubheadingWithoutTitleAndDate
    {B1 German Certificate} {Goethe Ins.}
    \CvSubSubheadingWithoutTitleAndDate
    {C1 IELTS Certificate} { IDP Education}
    \CvSubHeadingListEnd
%
%-----------------------------------------
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \CvSubHeadingListStart
   \item{
     \textbf{Languages}{: Python, R, C++, C, C\#, Java, Javascript, PHP, HTML, CSS, JQuery, SQL, VHDL}}
   \item{
    \textbf{Technologies}{: AUTOSSAR, OpenGL, GIT, Polarion, JIRA, TensorFlow}
   }  
 \CvSubHeadingListEnd


%-------------------------------------------
\end{document}
